DisCon Kids Pilot

### 2019-03-03 analysis/02_kids_600.Rmd
add plots to kids analysis file

ggplot() +
  geom_jitter(data = p1, aes(x = experiment, y = correct,  alpha = .2),width = .2,height = .01)+
  geom_pointrange(data = p2, aes(x = experiment, y = mean,  ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="",y="Proportion correct in training")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  scale_color_solarized()
```

@@

# BAyesian t-test by age group

@@

@@

model_data <- data%>%
  filter(phase == "test")%>%
  mutate(age_num = scale(age_num))

@@

>>>>

ggplot() +
  geom_jitter(data = p1, aes(x = experiment, y = correct,  alpha = .2),width = .2,height = .01)+
  geom_pointrange(data = p2, aes(x = experiment, y = mean,  ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  scale_color_solarized()
```

@@

# Bayesian t-test by age group

@@

# Comparison to chance based on model

```{r}
chance_data <- data %>%
  filter(phase != "training") %>%
  group_by(subage,subid) %>%
  summarise(correct = mean(correct_target1)) %>%
  mutate(comp_chance= ifelse(correct<1/3,0,1))

library(brms)

chance_model <- brm(comp_chance ~ 1,
                    data = chance_data, family = bernoulli(),
          control = list(adapt_delta = 0.95),
          sample_prior = F,
          save_all_pars = TRUE,
          iter = 2000)

summary(chance_model)

```{r}
bayesplot::mcmc_areas(as.array(chance_model), pars = c("b_Intercept"), prob = 0.95)+
  geom_vline(xintercept = 0, lty = 2, col = "black")+
  theme_few()
```

@@

model_data <- data%>%
  filter(phase != "training")%>%
  mutate(age_num = scale(age_num))

@@

# Check category, position and trial

## category effects
```{r proportion of choices}
cat_plot <- data %>%
  filter(phase == 'test')%>%
  group_by(target1,subid) %>%
  summarise(correct = mean(correct_target1))

cat_plot_mean <- cat_plot %>%
  group_by(target1) %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = cat_plot, aes(x = target1, y = correct,  alpha = .2, col = target1),width = .2,height = .01)+
  geom_pointrange(data = cat_plot_mean, aes(x = target1, y = mean,  ymin = ci_lower, ymax = ci_upper, col = target1),size = .8)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  scale_color_solarized()
```

## position effects
```{r proportion of choices}
pos_plot <- data %>%
  filter(phase == 'test')%>%
  group_by(pickPos,subid) %>%
  summarise(correct = mean(correct_target1))

pos_plot_mean <- pos_plot %>%
  group_by(pickPos) %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = pos_plot, aes(x = pickPos, y = correct,  alpha = .2, col = pickPos),width = .2,height = .01)+
  geom_pointrange(data = pos_plot_mean, aes(x = pickPos, y = mean,  ymin = ci_lower, ymax = ci_upper, col = pickPos),size = .8)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  scale_color_solarized()
```

## trial effects
```{r proportion of choices}
trial_plot <- data %>%
  filter(phase == 'test')

ggplot(data = trial_plot, aes(x = trial, y = correct_target1)) +
  geom_jitter(alpha = .2,width = .2,height = .01)+
  geom_smooth(method = "loess",  se = T, size = 1, col = "darkred", fill = "darkgreen", alpha = .5 )+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  scale_color_solarized()
```
